Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-06-17 manuscript.tex
Update Fig01 with 3D visualizations [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/b00473f3d253b202af4827cb50f0be832208e927.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/b00473f3d253b202af4827cb50f0be832208e927/checks
https://github.com/habi/acinar-analysis-manuscript/runs/946141662

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...9a5eb86d587fe4312a9e8baa931a147ef99ec199}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/9a5eb86d587fe4312a9e8baa931a147ef99ec199/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/9a5eb86d587fe4312a9e8baa931a147ef99ec199}{habi/acinar-analysis-manuscript@9a5eb86}
on June 14, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(9a5eb86)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(9a5eb86)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\begin{figure}
\hypertarget{fig:01}{%
\centering
\includegraphics{images/fig01.png}
\caption{Example images for each of the assessed time points.
A--D: Representative light microscopy images.
E--H: One slice of the tomographic data sets.
I--L: Middle slice of one of the extracted acini.
The extracted acinus is overlaid on the tomographic dataset.
Panels J and K also show the segmentation stopper at the left border of the image.
The shown images correspond to the middle slice of the full data sets used for the stereological analysis.
The scale bar was burnt in during preparation of the image stacks and is 100~μm long.
Panels A, E \& I: Day 4.
Panels B, F \& J: Day 10.
Panels C, G \& K: Day 21.
Panels D, H \& L: Day 60.}\label{fig:01}
}
\end{figure}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...b00473f3d253b202af4827cb50f0be832208e927}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b00473f3d253b202af4827cb50f0be832208e927/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b00473f3d253b202af4827cb50f0be832208e927}{habi/acinar-analysis-manuscript@b00473f}
on June 17, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(b00473f)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(b00473f)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\begin{figure}
\hypertarget{fig:01}{%
\centering
\includegraphics{images/fig01.png}
\caption{Example images for each of the assessed time points.
A--D: Representative light microscopy images.
E--H: One slice of the tomographic data sets.
I--L: Middle slice of one of the extracted acini.
The extracted acinus is overlaid on the tomographic dataset.
Panels J and K also show the segmentation stopper at the left border of the image.
The shown images correspond to the middle slice of the full data sets used for the stereological analysis.
The scale bar was burnt in during preparation of the image stacks and is 100~μm long.
Panels A, E \& I: Day 4.
Panels B, F \& J: Day 10.
Panels C, G \& K: Day 21.
Panels D, H \& L: Day 60.
Panel M: Three-dimensional visualization of the acini shown in panels I--L.}\label{fig:01}
}
\end{figure}
